<i>invivoPKfit</i> and <i>CvTdb</i> figures

### 2022-11-15 MainAnalysis.Rmd
Making analyze_pk_data() and fit_all() more modular by splitting out functions to get starting values, get upper bounds, and get lower bounds

---
title: "<i>invivoPKfit</i> and <i>CvTdb</i> figures"
author: "Christopher Cook"
date: "1/31/2022"
output:
  html_document: default
  word_document: default
---

@@

```{r, load_cvt, eval = TRUE}

### this block runs the model fits
# and does some pre-processing to clean up the data

# data <- read.csv("inst/ext/cvt_query_for_john_27may2021_v2.csv")
# data <- read.csv("inst/ext/cvtdb_invivopkfit_02242022.csv")
# data <- read.csv("inst/ext/cvtdb_invivopkfit_04142022.csv")
cvt.data <- read.csv("inst/ext/cvtdb_invivopkfit_04262022-2.csv")

### these compounds had no CAS in the cvtdb
# double check and they should not have been added
# so I removed them

cvt.data <- cvt.data %>%
  filter(analyte_name_original != "Methemoglobin") %>%
  filter(analyte_name_original != "N-desmethyltamoxifen")

### fix compound names
cvt.data$analyte_name_original[cvt.data$analyte_name_original == "Methyleugonal "] <- "Methyleugonal"
cvt.data$analyte_name_original[cvt.data$analyte_name_original == "benzo[a]pyrene"] <- "benzo(a)pyrene"
cvt.data$analyte_name_original[cvt.data$analyte_name_original == "2,4-D"] <- "2,4-Dichlorophenoxyacetic acid"
cvt.data$analyte_name_original[cvt.data$analyte_name_original == "Diclofenac"] <- "Hexobarbital"
cvt.data$analyte_name_original[cvt.data$analyte_name_original == "Pentadecafluorooctanoic acid"] <- "Perfluorooctanoic acid"
cvt.data$analyte_name_original[cvt.data$analyte_name_original == "3−hydroxybenzo[a]pyrene"] <- "3−hydroxybenzo(a)pyrene"

### make fk_reference_document equal fk_extraction document if fk_reference_document is NULL
cvt.data$fk_reference_document_id[cvt.data$fk_reference_document_id == "NULL"] <- 
  cvt.data$fk_extraction_document_id[cvt.data$fk_reference_document_id == "NULL"]

### this is basically my debug line,
# where I can focus on one problematic compound 
# and see what's going wrong
# data <- data %>% filter(dsstox_casrn == "68291-97-4" | dsstox_casrn == "82626-48-0")
# data <- data %>% filter(dsstox_casrn == "123-91-1")
```

@@

```{r, set_file_timestamp, eval = TRUE}
THIS.DATE <- "111022"
```

```{r, run_invivoPKfit_1comp, eval = FALSE}
### do 1-Compartment fit
system.time(PK.fit.table.1comp <- fit_all(
  data.set = cvt.data,
  model = "1compartment",
  modelfun = "analytic",
  compound.col = "analyte_name_original",
  dtxsid.col = "dsstox_substance_id",
  cas.col = "dsstox_casrn",
  reference.col = "fk_reference_document_id",
  species.col = "species",
  species.weight.col = "weight_kg",
  species.weight.units.default = "kg",
  dose.col = "dose_level_normalized",
  time.col = "time_hr",
  time.units.default = "hr",
  media.col = "conc_medium_normalized",
  media.units.default = "normalized",
  value.col = "conc",
  units.default = NA,
  route.col = "administration_route_normalized",
  source.col = "document_id",
  loq.col ="calc_loq",
  subject.default = NA,
  info.default = NA,
  suppress.messages = TRUE
))
write.csv(PK.fit.table.1comp[[1]], paste("inst/ext/PK.fit.table.1comp.",THIS.DATE,".csv",sep=""), row.names = FALSE)
write.csv(PK.fit.table.1comp[[2]], paste("inst/ext/processed.1comp.data.",THIS.DATE,".csv",sep=""), row.names = FALSE)
```

>>>>

---
title: "<i>invivoPKfit</i> and <i>CvTdb</i> figures"
author: "Christopher Cook, John Wambaugh, Caroline Ring"
date: "11/15/2022"
output:
  html_document: default
  word_document: default
---

@@

Read in CvTdb data.

```{r, load_cvt, eval = TRUE}
cvt.data <- read.csv("inst/ext/cvtdb_invivopkfit_04262022-2.csv")
```

A couple of compounds had no CAS in CvTdb. Upon double checking, they should not have been added. So remove them. (CLR 2022-11-15: it doesn't look like there are any of these)

```{r, cvt_remove_nocas}
cvt.data <- cvt.data %>%
  filter(analyte_name_original != "Methemoglobin") %>%
  filter(analyte_name_original != "N-desmethyltamoxifen")
```

Fix a few compound names.
```{r, cvt_fix_cpd_names}
cvt.data$analyte_name_original[cvt.data$analyte_name_original == "Methyleugonal "] <- "Methyleugonal"
cvt.data$analyte_name_original[cvt.data$analyte_name_original == "benzo[a]pyrene"] <- "benzo(a)pyrene"
cvt.data$analyte_name_original[cvt.data$analyte_name_original == "2,4-D"] <- "2,4-Dichlorophenoxyacetic acid"
cvt.data$analyte_name_original[cvt.data$analyte_name_original == "Diclofenac"] <- "Hexobarbital"
cvt.data$analyte_name_original[cvt.data$analyte_name_original == "Pentadecafluorooctanoic acid"] <- "Perfluorooctanoic acid"
cvt.data$analyte_name_original[cvt.data$analyte_name_original == "3−hydroxybenzo[a]pyrene"] <- "3−hydroxybenzo(a)pyrene"
```

if fk_reference_document is NULL, make fk_reference_document equal fk_extraction document. (CLR 2022-11-15: it doesn't look like there are any of these)

```{r}
cvt.data$fk_reference_document_id[cvt.data$fk_reference_document_id == "NULL"] <- 
  cvt.data$fk_extraction_document_id[cvt.data$fk_reference_document_id == "NULL"]
```

```{r}
### this is basically my debug line,
# where I can focus on one problematic compound 
# and see what's going wrong
# data <- data %>% filter(dsstox_casrn == "68291-97-4" | dsstox_casrn == "82626-48-0")
# data <- data %>% filter(dsstox_casrn == "123-91-1")
```

@@

Set a timestamp: today's date. (I am changing this to YYYYMMDD format -- better sorting by filename. -- CLR)

```{r, set_file_timestamp, eval = TRUE}
THIS.DATE <- "20221115"
```

Run a one-compartment fit on the data, and write out the results.

```{r, run_invivoPKfit_1comp, eval = FALSE}
### do 1-Compartment fit
system.time(PK.fit.table.1comp <- fit_all(
  data.set = cvt.data,
  model = "1compartment",
  modelfun = "analytic",
  compound.col = "analyte_name_original",
  dtxsid.col = "dsstox_substance_id",
  cas.col = "dsstox_casrn",
  reference.col = "fk_reference_document_id",
  species.col = "species",
  species.weight.col = "weight_kg",
  species.weight.units.default = "kg",
  dose.col = "dose_level_normalized",
  time.col = "time_hr",
  time.units.default = "hr",
  media.col = "conc_medium_normalized",
  media.units.default = "normalized",
  value.col = "conc",
  units.default = NA,
  route.col = "administration_route_normalized",
  source.col = "document_id",
  loq.col ="calc_loq",
  subject.default = NA,
  info.default = NA,
  suppress.messages = TRUE
))

write.csv(PK.fit.table.1comp[[1]], paste("inst/ext/PK.fit.table.1comp.",THIS.DATE,".csv",sep=""), row.names = FALSE)

write.csv(PK.fit.table.1comp[[2]], paste("inst/ext/processed.1comp.data.",THIS.DATE,".csv",sep=""), row.names = FALSE)
```
